### 2004-12-07 doc/Simulation_and_Control_using_Supremica/automationobjects.tex
*** empty log message ***

%% repositories
%%   non-hierarchical pool of automation objects
%%   may be share using the internet
%%   searching and sorting by multiple attributes/keys
%%   searching and sorting by services
It is envisioned that after the initial acceptance period
significant amount of automation objects are developed.
These are stored in the repositories for easy acess. The
repositories are non-hierarchical pools of automation
objects, probably implemented using database technology.
These repositories are prefferably shared over the internet.
The most important feature of the repositories is the
ability for extensinve search and sorting by multiple
attributes defined in the registry as well as the defined
services.

@@

The DE provides the tools and functions for the repository
handlig and automation object development. The user is able
to choose among the available automation objects from the
repository and include them in the application. While
working with the objects the user can activate different
services or bring up specific views and exchange the models
and controllers. User can also connect the views of the
different objects in the application. Working in this way
the user can build and tune the application to it's liking.

@@

While the user have one of the simulation models activated
the run-time is executing the code that simulates the
behaviour of the hardware that the object is supposed to
control. Switching to the model that talks to the process
interface issues a command to exchange the function blocks
in the run-time and results in the control of hardware
instead of the simulation of the control. This gives user
the freedom to incrementally develop large systems.

For example, consider a production plant that is connected
to the network of control computers. Engineers responsible
for each part can develop, tune and test their part on any
computer on the network. As each one switches to the model
that communcates with the hardware the plant becomes more
and more functional until it is fully operational.

To accomplish this the development environment uses the
database technology to hold the application data that is
shared. While working on the application the engineers can
acess this data from any computer on the network. The
application data includes the distribution configuration
governing which automation objects are run by which
computers on the network. By issuing the commands to the
run-time environment of the computer running the automation
object that is currently worked on, the development
environment allows the user to work on the whole application
from any computer on the network. This means that if
something goes wrong or software/equipment needs upgrading
anyone that can acess the application data can, from any
computer on the network, switch the model of the automation
object in question to simulation model so that the parts of
the plant that don't need the resource being upgraded in the
production can continue to function, resolv the problem or
perform the upgrade and finally switch back. This feature
can also be used for active monitoring, tuning and control
of the system by a human operator given that the views
implementing the human machine interface are developed.

>>>>

%% repositories
%%   non-hierarchical pool of automation objects
%%   may be share using the internet
%%   searching and sorting by multiple attributes/keys
%%   searching and sorting by services
It is envisioned that after the initial acceptance period
significant amount of automation objects are developed.
These are stored in the repositories for easy access. The
repositories are non-hierarchical pools of automation
objects, probably implemented using database technology.
These repositories are preferably shared over the internet.
The most important feature of the repositories is the
ability for extensive search and sorting by multiple
attributes defined in the registry as well as the defined
services.

@@

The DE provides the tools and functions for the repository
handling and automation object development. The user is able
to choose among the available automation objects from the
repository and include them in the application. While
working with the objects the user can activate different
services or bring up specific views and exchange the models
and controllers. User can also connect the views of the
different objects in the application. Working in this way
the user can build and tune the application to it's liking.

@@

While the user have one of the simulation models activated
the run-time is executing the code that simulates the
behavior of the hardware that the object is supposed to
control. Switching to the model that talks to the process
interface issues a command to exchange the function blocks
in the run-time and results in the control of hardware
instead of the simulation of the control. This gives user
the freedom to incrementally develop large systems.

For example, consider a production plant that is connected
to the network of control computers. Engineers responsible
for each part can develop, tune and test their part on any
computer on the network. As each one switches to the model
that communicates with the hardware the plant becomes more
and more functional until it is fully operational.

To accomplish this the development environment uses the
database technology to hold the application data that is
shared. While working on the application the engineers can
access this data from any computer on the network. The
application data includes the distribution configuration
governing which automation objects are run by which
computers on the network. By issuing the commands to the
run-time environment of the computer running the automation
object that is currently worked on, the development
environment allows the user to work on the whole application
from any computer on the network. This means that if
something goes wrong or software/equipment needs upgrading
anyone that can access the application data can, from any
computer on the network, switch the model of the automation
object in question to simulation model so that the parts of
the plant that don't need the resource being upgraded in the
production can continue to function, resolve the problem or
perform the upgrade and finally switch back. This feature
can also be used for active monitoring, tuning and control
of the system by a human operator given that the views
implementing the human machine interface are developed.

### 2004-12-07 doc/Simulation_and_Control_using_Supremica/introduction.tex
*** empty log message ***

%Define the problem.
Ever increasing competition forces companies to diversify
their product lines. To achieve customizable products the
companies require constantly changing and evolving
production plants. Such plants are called flexible
production plants. The plant is constantly adopted to the
products with the goal of production of highest quality
products in as little time as posibble. To achieve this the
software for the automatic control of such a plant has to be
developed and upgraded along with the plant. The problem is
that when using today established development methods this
upgrade is impossible without an interrupt of the production
that can last for several weeks in some cases.

To avoid the down time associated with the upgrade of the
control software in the production plants a more agile
architecture for the control software is needed. To be more
specific an object oriented architecutre and development
method are needed as opposed to the loop based architecture
and structured development method implemented with PLCs. The
advantages of object oriented software development are
reaped across the IT industry for quite some time now. Why
it has not been widely adopted in the automatic control
software development is for the most part because of the
high investment already made in the PLCs making the
companies reluctant to invest in yet another expensive
thechnology driven upgrade. In other words, as long as the
automation control problems in the existing plants are
possible to be solved with PLCs there will be no adoption of
object orented architectures. Another big reason for slow
adoption of object oriented development methods is the lack
of standard object oreinted platform suitable for the
automation software applications.

@@

%Introduce Function Blocks

%Introduce Automation Objects

>>>>

%Define the problem.
Ever increasing competition forces companies to diversify
their product lines. To achieve customizable products the
companies require constantly changing and evolving
production plants. Such plants are called flexible
production plants. The plant is constantly adopted to the
products with the goal of production of highest quality
products in as little time as possible. To achieve this the
software for the automatic control of such a plant has to be
developed and upgraded along with the plant. The problem is
that when using today established development methods this
upgrade is impossible without an interrupt of the production
that can last for several weeks in some cases.

To avoid the down time associated with the upgrade of the
control software in the production plants a more agile
architecture for the control software is needed. To be more
specific an object oriented architecture and development
method are needed as opposed to the loop based architecture
and structured development method implemented with PLCs. The
advantages of object oriented software development are
reaped across the IT industry for quite some time now. Why
it has not been widely adopted in the automatic control
software development is for the most part because of the
high investment already made in the PLCs making the
companies reluctant to invest in yet another expensive
technology driven upgrade. In other words, as long as the
automation control problems in the existing plants are
possible to be solved with PLCs there will be no adoption of
object oriented architectures. Another big reason for slow
adoption of object oriented development methods is the lack
of standard object oriented platform suitable for the
automation software applications. The latter reason is being
addressed by several vendors but their offerings are
proprietary, incompatible and only add-ons to the IEC 61131
standard which defines a non object oriented development
platform.

@@

%Introduce Function Blocks
The International Electrotechnical Commission (IEC) is making
an effort to standardize a platform for the software of next
generation of systems for industrial measurement and
control. The standard is named IEC 61499 and it defines the
architecture, software tool requirements and application
guidelines. The architecture defines object oriented
platform for distributable software components and is
described in more detail in chapter~\ref{functionblocks}.

%Introduce Automation Objects
The standard defines the common ground for the distributed
industrial control applications but it is not enough. To
ease the effective and rapid control application development
a more user friendly software objects are needed. The kind
of objects that will run on any IEC 61499 compatible system
but provide a greater support for the task of application
developing. That kind of objects are defined in
chapter~\ref{automationobjects}.
